\documentclass[a5paper, twoside]{report}
\usepackage[a5paper, top=1cm, inner=15mm, landscape]{geometry}
%\usepackage[ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage{multicol}

\pagestyle{plain}
%\geometry{twoside, paperwidth=100mm, paperheight=100mm, inner=15mm, outer=10mm, top=10mm, bottom=10mm}

\parindent0pt	

\pagestyle{empty}
\begin{document}

\textbf{{\LARGE Lassi / Sweet Lassi}}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\hrulefill
\vspace*{\fill}
\begin{multicols}{2}	


\begin{itemize}
\item $1\frac{1}{2}$ Yoghurt/Curd
\item $\frac{1}{4}$ Becher Milch
\item 4-5 EL Zucker
\item 2 Brisen Salz
\item $\frac{1}{4}$ EL Kardamompulver
 \item $\frac{1}{4}$ Becher Sahne
\item 1-2 Mandeln
\end{itemize}

\end{multicols}
\vfill
\newpage
\textbf{{\LARGE Zubereitung}}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hrulefill

\vspace*{\fill}
\begin{multicols}{2}
\columnseprule1pt

I used chilled curds, milk, cream.
Collect the cream that floats on top of boiled milk and store it in the fridge. Do not beat it to creamy consistency. Let it be in the curdled form itself.
In a mixie powder the sugar first. In a blender using the whipper blade beat the curd till it froths. Add the milk, powdered sugar, cardamom powder and whip till they all blend well.
Transfer to a pitcher. In a tall glass first pour the lassi to 1/4 th of the glass then add 2-3 tbsp cream. Again top with lassi to 1/2 and repeat adding cream. 
Pour the lassi to the top of the glass and top it further with cream and finely chopped almonds.\\

Notes:\\
Make sure that the curd is slightly sour else the lassi will taste like sweetened milk.\\
Powdering the sugar will help in blending well and prevents the lassi from being watered quickly.\\
If the ingredients are not cold enough add 2-3 ice cubes.\\
Adding a pinch or 2 of salt will enhance the sweetness of the lassi.\\
Do not beat the cream to smooth consistency. It should be in the curdled form so that you can feel it in your mouth while drinking the lassi.


\end{multicols}
\vfill
\end{document}